\LARGE How coexistence mechanisms mediate temporal stability

### 2015-04-02 manuscript/manuscript.Rmd
Fix subscript and add text on random resource pulse generation.

where $i$ denotes species, $D$ is the dormant (long-lived) biomass state, $N$ is the living biomass (fast-growing, shorter-lived) state, and $m$s are biomass loss rates. The growth rate of living biomass is a resource-dependent function, $f_{i}(R) = r_{i}e^{-\alpha_{i}e^{-\beta_{i}R}}$. Resource depletion is equal to the sum of each species' consumption, $\sum_{i=1,2}f(R)N_{i}$. Note that since transitions between $N$ and $D$ are pulsed, only biomass loss occurs throughout the season for $D$.

@@

Results
-------
### Storage effect model
Some preliminary results from running simulations of the storage effect version of the model at different levels of environmental cue variability ($\sigma_{E}$) and resource supply variability ($\sigma_{S}$). I ran 20 simulations at each combination of $\sigma_{E}$ and $\sigma_{S}$ shown in Figure~\ref{fig:storeEffSims} (the points are the means across the 20 simulations, each run for 2,000 time-steps, with the initial 1,000 time-steps discarded before calculating anything). There is a weak trend of community CV to saturate at high levels of resource supply variability (Figure~\ref{fig:storeEffSims}, top panel).

One of the things we are interested in is how well the community buffers itself against resource variability. Really I should calculate some kind of asynchrony metric, but for now I just looked at the ratio of the resource CV to the community CV (Figure~\ref{fig:storeEffSims}, bottom panel). Kind of difficult to interpret, but it is interesting that at high levels of variability in the environmental cue that drives the storage effect, the ratio decreases with resource supply variability. The opposite occurs at lower levels of variability in the environmental cue.

>>>>

where $i$ denotes species, $D$ is the dormant (long-lived) biomass state, $N$ is the living biomass (fast-growing, shorter-lived) state, and $m$s are biomass loss rates. The growth rate of living biomass is a resource-dependent function, $f_{i}(R) = r_{i}e^{-\alpha_{i}e^{-\beta_{i}R}}$. Resource depletion is equal to the sum of each species' consumption, $\sum_{i=1,2}f_{i}(R)N_{i}$. Note that since transitions between $N$ and $D$ are pulsed, only biomass loss occurs throughout the season for $D$.

@@

Results
-------
### Storage effect model

### 2015-04-02 manuscript/manuscript.tex
Fix subscript and add text on random resource pulse generation.

We start with a general consumer-resource model where the consumer can
be in one of two-states: a dormant state $D$ and a live state $N$
(Figure\textasciitilde{}\ref{fig:model}). Transitions between $N$ and
$D$ occur at discrete intervals $T$, so our model is formulated as
``pulsed differential equations" (Pachepsky et al. 2008, Mailleret and
Lemesle 2009). For clarity we refer to $T$ as years and the growing time
between years, $\tau$, as seasons. Seasonal (within-year) dynamics are
modeled as three differential equations:

@@

where $i$ denotes species, $D$ is the dormant (long-lived) biomass
state, $N$ is the living biomass (fast-growing, shorter-lived) state,
and $m$s are biomass loss rates. The growth rate of living biomass is a
resource-dependent function,
$f_{i}(R) = r_{i}e^{-\alpha_{i}e^{-\beta_{i}R}}$. For the resource
dynamics, whose state is denoted by $R$, we use a linear resource
renewal equation where $a$ scales resource turnover rate and $S$ is the
resource equilibrium when consumers are absent, and an offtake of the
resource equal to the sum of each species' consumption,
$\sum_{i=1,2}f(R)N_{i}$. Note that since transitions between $N$ and $D$
are pulsed, only biomass loss occurs throughout the season for $D$.

@@

where $D(T^-)$, $N(T^-)$, and $R(T^-)$ are the densities of each state
at the end of the year and $g$ is a time-fluctuating activation rate
that regulates how much dormant biomass is converted to growing-season
live biomass each year. Our formulation assumes that at the end of each
season all accumulated living biomass {[}$N(T^-)${]} is converted to
dormant biomass.

@@

Some preliminary results from running simulations of the storage effect
version of the model at different levels of environmental cue
variability ($\sigma_{E}$) and resource supply variability
($\sigma_{S}$). I ran 20 simulations at each combination of $\sigma_{E}$
and $\sigma_{S}$ shown in Figure\textasciitilde{}\ref{fig:storeEffSims}
(the points are the means across the 20 simulations, each run for 2,000
time-steps, with the initial 1,000 time-steps discarded before
calculating anything). There is a weak trend of community CV to saturate
at high levels of resource supply variability
(Figure\textasciitilde{}\ref{fig:storeEffSims}, top panel).

One of the things we are interested in is how well the community buffers
itself against resource variability. Really I should calculate some kind
of asynchrony metric, but for now I just looked at the ratio of the
resource CV to the community CV
(Figure\textasciitilde{}\ref{fig:storeEffSims}, bottom panel). Kind of
difficult to interpret, but it is interesting that at high levels of
variability in the environmental cue that drives the storage effect, the
ratio decreases with resource supply variability. The opposite occurs at
lower levels of variability in the environmental cue.

>>>>

We start with a general consumer-resource model where the consumer can
be in one of two-states: a dormant state $D$ and a live state $N$ (Fig.
1). Transitions between $N$ and $D$ occur at discrete intervals $T$, so
our model is formulated as ``pulsed differential equations" (Pachepsky
et al. 2008, Mailleret and Lemesle 2009). For clarity we refer to $T$ as
years and the growing time between years, $\tau$, as seasons. Seasonal
(within-year) dynamics are modeled as three differential equations:

@@

where $i$ denotes species, $D$ is the dormant (long-lived) biomass
state, $N$ is the living biomass (fast-growing, shorter-lived) state,
and $m$s are biomass loss rates. The growth rate of living biomass is a
resource-dependent function,
$f_{i}(R) = r_{i}e^{-\alpha_{i}e^{-\beta_{i}R}}$. Resource depletion is
equal to the sum of each species' consumption,
$\sum_{i=1,2}f_{i}(R)N_{i}$. Note that since transitions between $N$ and
$D$ are pulsed, only biomass loss occurs throughout the season for $D$.

@@

where $D(T^-)$, $N(T^-)$, and $R(T^-)$ are the densities of each state
at the end of the year and $g$ is a time-fluctuating activation rate
that regulates how much dormant biomass is converted to growing-season
live biomass each year. $R(T^+)$ is a randomly generated resource pulse
from a log-normal distribution with mean $\mu_{R}$ and standard
deviation $\sigma_{R}$. Our formulation assumes that at the end of each
season all accumulated living biomass {[}$N(T^-)${]} is converted to
dormant biomass.

@@
